### 2014-03-08 src/conclusion.Rnw
update

\begin{enumerate}
\item [x] For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
\item [TODO] We should check if the distribution significantly different too.
\item [DONE] Use sampling
\item [DONE] Check on randoop samples too
\item [NO] Implement bomb (athrow) and see its mutation score, and see how close it comes.
\item [DONE] Compare random selection with class, method, and mutagen sampling.
\item [TODO] Report time for each, as cost.
\item [TODOX] Find the mutant count to LOC multiplier, and use it to get the probability of choosing for each project.
\end{enumerate}

>>>>

% For op-selection to work, the distributions of mutations across different projects has to be similar enough. This can be checked by t-test.
% For mutant clustering
%TODO Report time for each, as cost.

Our analysis suggests that random sampling of mutants can help reduce the computational requirements to an extremely large extant while still staying within acceptable accuracy limits.
An interesting finding is that statement deletion did produce as good accuracy in predicting final mutation score as random sampling techniques that offered comparable mutation reduction.
